Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-30 review_article.Rmd
typo in bib
typo in abstract

\section*{Abstract}
Choropleth maps are widely used in cancer atlases, and traditionally communicate cancer statistics over geographic domains. The type of statistic displayed varies immensely, and effective choices can assist in the understanding of impact of cancer on a population. Atlases have moved from print media to web format, and the availability of graphical user interfaces, and user interaction and animation, greatly enhance the ability to communicate more information and positively engage readers. More use of alternatives to choropleth maps, such as cartograms, could be employed in online atlases, to better representation of spatial distributions, and show statistics on small areas. This is especially true for the geography of Australia, where the population is concentrated is small areas along the coastlines.

@@

# Alternative to choropleths {#ch:alternatives}

## Micromaps

Choropleths are uni-variate displays, they do not inherently support multi-dimensionality.
This makes it difficult to pair demographic, environmental and other factors with spatial distributions.

<!--
Visualizing Data Patterns with Micromaps.
Two new templates for epidemiology applications: linkedmicromap plots and conditioned choropleth maps-->

@@

# User interactions with maps {#ch:interacting}

>>>>

\section*{Abstract}
Choropleth maps are widely used in cancer atlases, and traditionally communicate cancer statistics over geographic domains. The type of statistic displayed varies immensely, and effective choices can assist in the understanding of impact of cancer on a population. Atlases have moved from print media to web format, and the availability of graphical user interfaces, and user interaction and animation, greatly enhance the ability to communicate more information and positively engage readers. More use of alternatives to choropleth maps, such as cartograms, could be employed in online atlases, for better representation of spatial distributions, and show statistics on small areas. This is especially true for the geography of Australia, where the population is concentrated is small areas along the coastlines.

@@

# Alternatives to choropleths {#ch:alternatives}

@@

# User interaction {#ch:interacting}
